\begin{thebibliography}{99}

\bibitem{ABK_hyb_sys} {\it Куржанский~А.Б., Варайя~П.} Задачи динамики и
управления в гибридных системах // Труды международного семинара
“Теория управления и теория обобщенных решений уравнений
Гамильтона-Якоби”. Екатеринбург: Изд-во Уральского университета,
2005. c.26--33.

\bibitem{ABK_upr_i_nabl} {\it Куржанский~А.Б.} Управление и наблюдение в
условиях неопределенности. М.: Наука, 1977.

\bibitem{solve_article} {\it Куржанский~А.Б., Точилин~П.А.} Слабо
инвариантные множества гибридных систем // Дифференциальные
уравнения. 2008. т.~44, N11.

\bibitem{Pshenichnyi} {\it Пшеничный~Б.Н.} Выпуклый анализ и
экстремальные задачи. М.: Наука, 1980.

\bibitem{Rokafellar} {\it Рокафеллар~Р.} Выпуклый анализ. М.: Мир, 1973.

\bibitem{Branicky} {\it Branicky~M.S., Borkar~V.S., Mitter~S.M.} A
unified framework for hybrid control: model and optimal control
theory. // IEEE transactions on automatic control, 43/1 p.31--45,
1998.

\bibitem{ABK_ellipse_for_reach_under_state_constraints} {\it
Kurzhanski~A.B., Varaiya~P.} Ellipsoidal techniques for
reachability under state constraints.// SIAM Journal on Control.
2003. V.45. N.4. p.1369--1394.

\bibitem{ABK_internal_approx} {\it Kurzhanski~A.B., Varaiya~P.}
Ellipsoidal techniques for reachability analysis. Internal
approximation // System and Control Letters. 2000. V.41.
p.201--211.

\bibitem{ABK_int_i_ext_approx} {\it Kurzhanski~A.B., Varaiya~P.}
Ellipsoidal techniques for reachability analysis. Part I: External
approximations. Part II: Internal approximations. Box-valued
constraints // Optimization methods and software. 2002. V.17.
p.177--237.

\bibitem{Liberzon} {\it Liberzon~D.} Switching in systems and control. Boston: Birkh\"{a}user, 2003.

\bibitem{Shumacher} {\it Van~der~Schaft~A., Schumacher~H.} An introduction to hybrid
dynamical systems. Lecture Notes in Control and Information
Sciences. N251. Springer, 2000.
 
\end{thebibliography}

